---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sae.projection

<!-- badges: start -->

[![CRAN status](https://www.r-pkg.org/badges/version/sae.projection)](https://CRAN.R-project.org/package=sae.projection) [![R-CMD-check](https://github.com/Alfrzlp/sae.projection/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Alfrzlp/sae.projection/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

## Author

Azka Ubaidillah, Ridson Al Farizal P

## Maintainer

Ridson Al Farizal P [ridsonap\@bps.go.id](mailto:ridsonap@bps.go.id)

## Description

The goal of **sae.projection** is to provide tools for performing **Small Area Estimation (SAE)** using projection-based methods. This approach is particularly effective for generating reliable domain-level estimates in situations where sample sizes are too small for direct estimation. By utilizing auxiliary information and statistical models, the package improves the precision and accuracy of small area estimates.

## Installation

You can install the development version of sae.projection from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Alfrzlp/sae.projection")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(sae.projection)
library(dplyr)
```

### Logistic Model

```{r example1}
df_res <- projection_estimator(
   formula = unemployment ~ edu + sex + age + head,
   domain = c('prov', 'regency'),
   weight = 'weight',
   data_model = df_svy2,
   data_proj = df_svy1,
   model = 'logistic',
   cutoff = 'optimum'
)
```

### Linear Model

```{r example2}
df_svy2_new <- df_svy2 %>% dplyr::filter(!is.na(income))

m2 <- projection_estimator(
  formula = income ~ edu + sex + age + head,
  domain = c('prov', 'regency'),
  weight = 'weight',
  data_model = df_svy2_new,
  data_proj = df_svy1,
  model = 'linear'
)
```
